
```{r}
#libraries
library(pacman)
p_load(tidyverse, here, posterior, cmdstanr, boot, brms)

```

# Part 1

You have to design a study (aka plan the number of trials) assuming that people are using a reinforcement learning process to pick between 2 stimuli. In this study you expect there to be 2 conditions and the 1 participant playing the game will vary its learning rate between conditions. The difference in learning rate is .2: condition 1 has x - .1 and condition 2 x + .1, with x = 0.7. The temperature is the same: 0.5.
Identify a feasible number of trials and motivate it.

## Simulating data

### Functions 
```{r}
#Creating softmax function to select choice among more options
softmax <- function(x,tau) {
  outcome = 1/(1+exp(-tau*x))
  return(outcome) #the choice that is made
}

#Create update function, that simulates reinforcement learning
ValueUpdate = function(value, alpha, choice, feedback){
  #predicted reward + lr * prediction error
  v1 <- value[1] + alpha * (1-choice) * (feedback - value[1]) 
  v2 <- value[2] + alpha * (choice) * (feedback - value[2])
  updatedValue <- c(v1, v2)
  
  #value = expected reward, feedback = reward, choice = slot machine
}

```


###Defining variables and preparing data frame
```{r}
#defining intial values
value <- c(0, 0) 
alpha <- c(0.6, 0.8)
temperature <- 0.5
choice <- 0
feedback <- -1
p <- 0.75
trials = 10000

#Intialising data frame
d <- tibble(choice = rep(NA, trials),
		value1 = rep(NA, trials), 
		value2 = rep(NA, trials),
		feedback = rep(NA, trials), 
		condition = rep(NA, trials), 
		trial = rep(NA, trials))

d2 <- tibble(choice = rep(NA, trials),
		value1 = rep(NA, trials), 
		value2 = rep(NA, trials),
		feedback = rep(NA, trials), 
		condition = rep(NA, trials), 
		trial = rep(NA, trials))

```


###Part 1: Simulating data 
```{r}
#Define the bot mechanism a.k.a. the two arm bandit
Bot <- rbinom(trials, 1, p)

#Condition 1
#Loop trough conditions and trials and save values
current_alpha <- alpha[1] #save lr for current condition
for(i in 1:trials){
	choice <- rbinom(1, 1 ,softmax(value[2] - value[1], temperature))
	feedback <- ifelse(Bot[i] == choice, 1, -1)
	value <- ValueUpdate(value, current_alpha, choice, feedback)
	d$choice[i] <- choice
	d$value1[i] <- value[1]
	d$value2[i] <- value[2]
	d$feedback[i] <- feedback
	d$condition[i] <- current_alpha
	d$trial[i] <- i
}
#Condition 2
#reset values
choice <- 0
feedback <- -1
value <- c(0, 0) 

#Loop trough conditions and trials and save values
current_alpha <- alpha[2] #save lr for current condition
for(i in 1:trials){
	choice <- rbinom(1, 1 ,softmax(value[2] - value[1], temperature))
	feedback <- ifelse(Bot[i] == choice, 1, -1)
	value <- ValueUpdate(value, current_alpha, choice, feedback)
	d2$choice[i] <- choice
	d2$value1[i] <- value[1]
	d2$value2[i] <- value[2]
	d2$feedback[i] <- feedback
	d2$condition[i] <- current_alpha
	d2$trial[i] <- i
}

#Rbind the two data frames
d <- rbind(d, d2)  

#Manipulate choice to be in the range of 1 and 2
d$choice <- ifelse(d$choice==0, 1, 2)

d$con1 = ifelse(d$condition == 0.6, 1, 0)
d$con2 = ifelse(d$condition == 0.8, 1, 0)

```


```{r}
#path <- 'INSERT PATH'

write.csv(d,paste("data/",trials,"trials_RL_data.csv", sep=""), row.names = FALSE)
```

###Part 2: Simulating data for iterated design
```{r}
#defining intial values
session_numbers = c(5, 10, 15, 25, 50, 75, 100, 250)
trials = 50
alpha <- c(0.6, 0.8)
temperature <- 0.5
p <- 0.75

#Intialising data frame
d <- tibble(choice = rep(NA, trials),
		value1 = rep(NA, trials), 
		value2 = rep(NA, trials),
		feedback = rep(NA, trials), 
		condition = rep(NA, trials), 
		trial = rep(NA, trials), 
		session = rep(NA, trials), 
		session_number = rep(NA, trials))

d2 <- tibble(choice = rep(NA, trials),
		value1 = rep(NA, trials), 
		value2 = rep(NA, trials),
		feedback = rep(NA, trials), 
		condition = rep(NA, trials), 
		trial = rep(NA, trials), 
		session = rep(NA, trials), 
		session_number = rep(NA, trials))

for (session_number in session_numbers) {
  print(session_number)
  for (session in 1:session_number) {
    #Condition 1
    #reset values
    choice <- 0
    feedback <- -1
    value <- c(0, 0) 
    
    #Loop trough conditions and trials and save values
    for(i in 1:trials){
      print(c('Session number', session, session_number, 'Condition 1', i))
    	choice <- rbinom(1, 1 ,softmax(value[2] - value[1], temperature))
    	feedback <- ifelse(Bot[i] == choice, 1, -1)
    	value <- ValueUpdate(value, alpha[1], choice, feedback)
    	d$choice[i] <- choice
    	d$value1[i] <- value[1]
    	d$value2[i] <- value[2]
    	d$feedback[i] <- feedback
    	d$condition[i] <- alpha[1]
    	d$trial[i] <- i
    	d$session[i] <- session
    	d$session_number[i] <- session_number
    }
    #Condition 2
    #reset values
    choice <- 0
    feedback <- -1
    value <- c(0, 0) 
    
    #Loop trough conditions and trials and save values
    for(i in 1:trials){
      print(c('Session number', session, session_number, 'Condition 2', i))
    	choice <- rbinom(1, 1 ,softmax(value[2] - value[1], temperature))
    	feedback <- ifelse(Bot[i] == choice, 1, -1)
    	value <- ValueUpdate(value, alpha[2], choice, feedback)
    	d2$choice[i] <- choice
    	d2$value1[i] <- value[1]
    	d2$value2[i] <- value[2]
    	d2$feedback[i] <- feedback
    	d2$condition[i] <- alpha[2]
    	d2$trial[i] <- i
    	d2$session[i] <- session
    	d2$session_number[i] <- session_number
    }
    #Rbind the two data frames
    d <- rbind(d, d2)
    	
    #bind with previous data
    if(exists("iterated_data")){iterated_data <- rbind (iterated_data, d)} else {iterated_data <- d
    }
  }
} 

#Manipulate choice to be in the range of 1 and 2
iterated_data$choice <- ifelse(iterated_data$choice==0, 1, 2)

#add condition columns dummy coded
iterated_data$con1 = ifelse(iterated_data$condition == 0.6, 1, 0)
iterated_data$con2 = ifelse(iterated_data$condition == 0.8, 1, 0)


```

```{r}
#path <- 'INSERT PATH'
write.csv(iterated_data,paste("data/","iterated_RL_data.csv", sep=""), row.names = FALSE)
```
