---
title: "Assignment_3_ACM"
output: html_document
date: '2022-03-30'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Preprocessing
```{r}
#load packages
library(pacman)
p_load(tidyverse, here, posterior, cmdstanr, boot, brms)

#Load data
data <- read.csv("data/sc_schizophrenia.csv")
```

```{r}
#Adding variables
data <- data %>%
  mutate(Change = FirstRating - SecondRating) %>%
  mutate(Group = as.factor(ifelse(ID >=200, "C", "S"))) %>%
  mutate(Feedback = FirstRating - OtherRating)

#Remove NA's
data <- na.omit(data)

#Creating two new variables to input to the model 
data$schizo <- ifelse(data$Group== "S", 1, 0)
data$control <- ifelse(data$Group== "C", 1, 0)
```

# Plot exploration
```{r}
#Feedback for the two groups 
ggplot(data, aes(x=Group, y=Feedback, fill = Group)) +
  geom_bar(stat = "summary", fun.y = "mean") 

#Correlation btw. feedback and change (for controls and schizophrenics
ggplot(data, aes(x=Feedback, y=Change, fill = Group)) +
  facet_wrap(~ Group) + 
  geom_bar(stat = "summary", fun.y = "mean") +
  theme_bw() + 
  theme(legend.position="none") +
  labs(title = 'Correlation btw. feedback and change (for controls and schizophrenics)')

#positive correlation. But individual differences:
ggplot(data, aes(x=Feedback, y= Change, col=Group)) +
  geom_point() +
  facet_wrap(~ID) +
  labs(title = 'Individual correlations btw. feedback and change')

#individual differences in how the scale is used + restrictions (see notes):
ggplot(data, aes(x=FirstRating, y= Feedback, col=Group)) +
  geom_point() +
  facet_wrap(~ID) +
  labs(title = 'Individual correlations btw. first rating and feedback')
```


#Simple Bayes for a single participant
```{r}
#Select data for single object 
data_s <- data[data$ID=="103",]

#Create data 
data_single <- list(
      N = max(data_s$Trial_Round2), 
      y = data_s$SecondRating/9,
      SourceSelf = data_s$FirstRating/9,
      SourceOther = data_s$OtherRating/9
    )
```


```{r}
#Import stan-file
file_simple <- file.path("W8_simpleBayes.stan")

#Compiling
mod_simple <- cmdstan_model(file_simple, cpp_options = list(stan_threads = TRUE), pedantic = TRUE)

```

```{r}
#Sampling
samples_simple <- mod_simple$sample(
    data = data_single,
    fixed_param = FALSE,
    seed = 123,
    chains = 2,
    parallel_chains = 2,
    threads_per_chain = 2,
    iter_warmup = 1000,
    iter_sampling = 1000,
    refresh = 1000,
    max_treedepth = 20,
    adapt_delta = 0.99)

#Save draws
draws_df <- as_draws_df(samples_simple$draws())

#Print model summary
samples_simple$summary()

```


```{r}
#Plotting model quality
ggplot(draws_df, aes(.iteration, sigma, group=.chain, color=.chain)) +
geom_line()+
theme_classic()


#Print model diagnostics
samples_simple$cmdstan_diagnose()
```

#Simple Bayes for all participants, full pooling
```{r}
#Create data 
data_all <- list(
      N = length(data$SecondRating), 
      y = data$SecondRating/9,
      SourceSelf = data$FirstRating/9,
      SourceOther = data$OtherRating/9
    )
```


```{r}
#Sampling
samples_simple <- mod_simple$sample(
    data = data_all,
    fixed_param = FALSE,
    seed = 123,
    chains = 2,
    parallel_chains = 2,
    threads_per_chain = 2,
    iter_warmup = 1000,
    iter_sampling = 1000,
    refresh = 1000,
    max_treedepth = 20,
    adapt_delta = 0.99)

#Save draws
draws_df <- as_draws_df(samples_simple$draws())

#print model summary
samples_simple$summary()

```

```{r}
#Plotting model quality
ggplot(draws_df, aes(.iteration, sigma, group=.chain, color=.chain)) +
geom_line()+
theme_classic()

#Print model diagnostics
samples_simple$cmdstan_diagnose()
```

#Weighted Bayes for a single participant

```{r}
#Import stan-file
file <- file.path("W8_weightedBayes_single.stan")

#Compiling
mod_weighted <- cmdstan_model(file, cpp_options = list(stan_threads = TRUE), pedantic = TRUE)

```

```{r}
#Sampling
samples_weighted <- mod_weighted$sample(
    data = data_single,
    fixed_param = FALSE,
    seed = 123,
    chains = 2,
    parallel_chains = 2,
    threads_per_chain = 2,
    iter_warmup = 1000,
    iter_sampling = 1000,
    refresh = 1000,
    max_treedepth = 20,
    adapt_delta = 0.99)

#Save draws
draws_df <- as_draws_df(samples_weighted$draws())

#Print model summary
samples_simple$summary()
```

```{r}
#Plotting model quality for weight1
ggplot(draws_df, aes(.iteration, weight1, group=.chain, color=.chain)) +
geom_line()+
theme_classic()

#Plotting model quality for weight2
ggplot(draws_df, aes(.iteration, weight2, group=.chain, color=.chain)) +
geom_line()+
theme_classic()

#Print model diagnostics
samples_simple$cmdstan_diagnose()
```

#Weighted Bayes for all participants, multi-level model

```{r}
#Create data 
choices <- data %>% 
  subset(select=c(ID, SecondRating))%>%
  group_by(ID)%>%
  mutate(row = row_number()) %>% 
  pivot_wider(names_from = ID, values_from = SecondRating) %>%
  select(!(row))

SourceSelfs <- data %>% 
  subset(select=c(ID, FirstRating))%>%
  group_by(ID)%>%
  mutate(row = row_number()) %>% 
  pivot_wider(names_from = ID, values_from = FirstRating) %>%
  select(!(row))

SourceOthers <- data %>% 
  subset(select=c(ID, OtherRating))%>%
  group_by(ID)%>%
  mutate(row = row_number()) %>% 
  pivot_wider(names_from = ID, values_from = OtherRating) %>%
  select(!(row))

#Trying to subset data
data_all_levels <- list(
      trials = max(data$Trial_Round2), 
      participants = length(unique(data$ID[data$ID %in% c(101, 103)])), #length(unique(data$ID)),
      choice = choices[, c('101', '103')]/9,
      SourceSelf = SourceSelfs[, c('101', '103')]/9,
      SourceOther = SourceOthers[, c('101', '103')]/9#,
      #schizo = data$schizo[data$ID %in% c(101, 103, 317)],
      #control = data$control[data$ID %in% c(101, 103, 317)]
    )

data_all_levels <- list(
      trials = max(data$Trial_Round2), 
      participants = length(unique(data$ID)),
      choice = choices/9,
      SourceSelf = SourceSelfs/9,
      SourceOther = SourceOthers/9
    )

```

```{r}
#Import stan-file
file <- file.path("W8_weightedBayes.stan")

#Compiling
mod_weighted <- cmdstan_model(file, cpp_options = list(stan_threads = TRUE), pedantic = TRUE)

```

```{r}
#Sampling
samples_weighted <- mod_weighted$sample(
    data = data_all_levels,
    fixed_param = FALSE,
    seed = 123,
    chains = 2,
    parallel_chains = 2,
    threads_per_chain = 2,
    iter_warmup = 500,
    iter_sampling = 500,
    refresh = 10,
    max_treedepth = 15,
    adapt_delta = 0.99)

```


```{r}
#Save draws
draws_df <- as_draws_df(samples_weighted$draws())

#Print model summary
samples_weighted$summary()
```


##Plotting posteriors
```{r}
#Plotting prior and posterior for weights: Has the model learned from the data? 
ggplot(draws_df) +
  geom_density(aes(w1), fill="blue", alpha=0.3) + 
  geom_density(aes(w1_prior_t), fill="red", alpha=0.3) +   xlab("w1") +
  ylab("Posterior Density") +
  theme_classic()

#Plotting prior and posterior for weights: Has the model learned from the data? 
ggplot(draws_df) +
  geom_density(aes(w2), fill="blue", alpha=0.3) + 
  geom_density(aes(w2_prior_t), fill="red", alpha=0.3) +   xlab("w2") +
  ylab("Posterior Density") +
  theme_classic()

#Plotting posteriors for sigma
ggplot(draws_df) + 
    geom_density(aes(sigma), color = 'blue')

#Plotting posteriors for tau
ggplot(draws_df) + 
    geom_density(aes(`tau[1]`), color = 'blue') + 
    geom_density(aes(`tau[2]`), color = 'green')

#Plotting posterior predictions vs. actual ratings
ggplot() + 
  geom_histogram(aes(data$SecondRating[data$ID == 103]), color="darkblue", fill="blue", alpha=0.3) + 
  geom_histogram(aes(round(draws_df$`posterior_preds[1]`*9, 0)[1:153]), color="green", fill="green", alpha=0.3) + 
  xlab("Predicted ratings out of 137 trials") + 
  ylab("Posterior Density") + 
  theme_classic()


#Prior and posterior predictions for participant 1
ggplot(draws_df) +
#  geom_histogram(aes(data_all_levels$choice[1]*9)) + 
  geom_histogram(aes(`posterior_preds[1]`*9),
  color="darkblue", fill="blue", alpha=0.3) + xlab("Predicted ratings out of 137 trials") + 
  geom_histogram(aes(`prior_preds[1]`*9),
  color="darkblue", fill="red", alpha=0.3) + xlab("Predicted ratings out of 137 trials") + 
  ylab("Posterior Density") + 
  theme_classic() + 
  labs(title = 'Prior and posterior predictions for participant 103')
```

```{r}
#Plotting model quality for weight1
ggplot(draws_df, aes(.iteration, weight1M, group=.chain, color=.chain)) +
geom_line()+
theme_classic()

#Plotting model quality for weight2
ggplot(draws_df, aes(.iteration, weight2M, group=.chain, color=.chain)) +
geom_line()+
theme_classic()

#Print model diagnostics
samples_weighted$cmdstan_diagnose()
```


#Weighted Bayes for all participants with advanced model (two levels)

```{r}
#Import stan-file
file <- file.path("W8_weightedBayes_advanced.stan")

#Compiling
mod_weighted <- cmdstan_model(file, cpp_options = list(stan_threads = TRUE), pedantic = TRUE)

```

```{r}
#Sampling
samples_weighted <- mod_weighted$sample(
    data = data_all_levels,
    fixed_param = FALSE,
    seed = 123,
    chains = 2,
    parallel_chains = 2,
    threads_per_chain = 2,
    iter_warmup = 1000,
    iter_sampling = 1000,
    refresh = 10,
    max_treedepth = 20,
    adapt_delta = 0.99)

#Save draws
draws_df <- as_draws_df(samples_weighted$draws())

#Print model summary
samples_simple$summary()

```

```{r}
#Prior and posterior predictions for participant 1
ggplot(draws_df) + 
  geom_histogram(aes(`posterior_preds`*9),
  color="darkblue", fill="blue", alpha=0.3) + xlab("Predicted ratings out of 137 trials") + 
  geom_histogram(aes(`prior_preds[137,1]`*9),
  color="darkblue", fill="red", alpha=0.3) + xlab("Predicted ratings out of 137 trials") + 
  ylab("Posterior Density") + 
  theme_classic() + 
  labs(title = 'Prior and posterior predictions for participant 1s trial 137')

```

```{r}
#Plotting model quality for weight1
ggplot(draws_df, aes(.iteration, weight1, group=.chain, color=.chain)) +
geom_line()+
theme_classic()

#Plotting model quality for weight2
ggplot(draws_df, aes(.iteration, weight2, group=.chain, color=.chain)) +
geom_line()+
theme_classic()

#Print model diagnostics
samples_simple$cmdstan_diagnose()
```

#Compare model
```{r}
#Example code from Ricci
Loo1 <- samples1$loo(save_psis = TRUE, cores = 3)
plot(Loo1)

Loo2 <- samples2$loo(save_psis = TRUE, cores = 2)
plot(Loo2)

d$diff_elpd <-
  Loo2$pointwise[, "elpd_loo"] -
  Loo1$pointwise[, "elpd_loo"]

p1 <- ggplot(d, aes(x = trial, y = diff_elpd)) +
  geom_point(alpha = .1) +
  xlim(.5,1.01) +
  ylim(-1.5,1.5) +
  geom_hline(yintercept=0, color="red", linetype="dashed") +
  theme_bw()
```


---NOTES FROM CLASS

change ~ feedback
, so:
2rating ~ logit(1rating) + logit(otherrating)

^^ but this has issues!:

BUT BIAS/POTENTIAL CONFOUND: not all feedbacks are possible! (e.g. if rate 8, can only get negative (or 0) feedback)
- reg to the mean? -> how to discriminate btw going down from an 8 rating due to reg to mean, or due to conformity?


SECOND POINT:
prev model was Bernoulli, 0 or 1
But now we need to change the family/shape of the outcome
recommended for assignment:
- go with normal distribution (not unproblematic, since it's discrete data... but for now, fuck it).
- a function of mu (mean expected outcome) and sigma (not part of the model).
mu is logit(first rating) + logit(peerrating). deterministic in simple Bayes, just one value.
Stan doesn't like sigma of 0...
We should put sigma in as a parameter to be estimated! It's the avg error the model is making when predicting the data!
So the parameters (parameters to be estimated) AND model (form of the model) part of stan have to be filled. A model that actually estimates sigma.

we should not have fixed parameters = TRUE, since sigma isn't fixed






BIASES:
- ID plots also show: people differ in how much they use the rating scale





