---
title: "Assignment_4_ACM_TRS"
author: "KK"
date: '2022-04-26'
output: html_document
---

# Preprocessing
```{r}
#load packages
library(pacman)
p_load(tidyverse, here, posterior, cmdstanr, boot, brms, patchwork)

#Load data
data <- read.csv("data/sc_schizophrenia.csv")
```

```{r}
#Adding variables
data <- data %>%
  mutate(Change = FirstRating - SecondRating) %>%
  mutate(Group = as.factor(ifelse(ID >=200, "C", "S"))) %>%
  mutate(Feedback = FirstRating - OtherRating)

#Remove NA's
data <- na.omit(data)

#Creating two new variables to input to the model 
data$schizo <- ifelse(data$Group== "S", 1, 0)
data$control <- ifelse(data$Group== "C", 1, 0)
```

# Plot exploration of data
```{r}
#Feedback for the two groups 
ggplot(data, aes(x=Group, y=Feedback, fill = Group)) +
  geom_bar(stat = "summary", fun.y = "mean") 

#Correlation btw. feedback and change (for controls and schizophrenics
ggplot(data, aes(x=Feedback, y=Change, fill = Group)) +
  facet_wrap(~ Group) + 
  geom_bar(stat = "summary", fun.y = "mean") +
  theme_bw() + 
  theme(legend.position="none") +
  labs(title = 'Correlation btw. feedback and change (for controls and schizophrenics)')

#positive correlation. But individual differences:
ggplot(data, aes(x=Feedback, y= Change, col=Group)) +
  geom_point() +
  facet_wrap(~ID) +
  labs(title = 'Individual correlations btw. feedback and change')

#individual differences in how the scale is used + restrictions (see notes):
ggplot(data, aes(x=FirstRating, y= Feedback, col=Group)) +
  geom_point() +
  facet_wrap(~ID) +
  labs(title = 'Individual correlations btw. first rating and feedback')
```

#Simple Bayes for one single participant, 103
```{r}
#Select data for single object 
data_s <- data[data$ID=="103",]

#Create data 
data_single <- list(
      N = max(data_s$Trial_Round2), 
      y = data_s$SecondRating/9,
      SourceSelf = data_s$FirstRating/9,
      SourceOther = data_s$OtherRating/9
    )
```

```{r}
#Import stan-file
file_simple <- file.path("W8_simpleBayes.stan")

#Compiling
mod_simple <- cmdstan_model(file_simple, cpp_options = list(stan_threads = TRUE), pedantic = TRUE)
```

```{r}
#Sampling
samples_simple <- mod_simple$sample(
    data = data_single,
    fixed_param = FALSE,
    seed = 123,
    chains = 2,
    parallel_chains = 2,
    threads_per_chain = 2,
    iter_warmup = 1000,
    iter_sampling = 1000,
    refresh = 1000,
    max_treedepth = 20,
    adapt_delta = 0.99)

#Save draws
simple_draws_df_single <- as_draws_df(samples_simple$draws())

#Print model summary
samples_simple$summary()
```

```{r}
#Plotting model quality
ggplot(draws_df_single_simple, aes(.iteration, sigma, group=.chain, color=.chain)) +
geom_line()+
theme_classic()

#Print model diagnostics
samples_simple$cmdstan_diagnose()
```

##Selecting 10 participants to run the analyses on to save time
```{r}
#selecting 10 participants 
the_selected_ones <- c(head(unique(data$ID), n =5), tail(unique(data$ID), n =5))

#subsetting data for the selected participants
data_subset <- data[data$ID %in% the_selected_ones,]
```

#Simple Bayes for all participants, full pooling
```{r}
#Create data 
some_simple_data <- list(
  N = length(data_subset$SecondRating), 
  y = data_subset$SecondRating/9,
  SourceSelf = data_subset$FirstRating/9,
  SourceOther = data_subset$OtherRating/9
  )
```


```{r}
#Sampling
samples_simple <- mod_simple$sample(
    data = some_simple_data,
    fixed_param = FALSE,
    seed = 123,
    chains = 2,
    parallel_chains = 2,
    threads_per_chain = 2,
    iter_warmup = 500,
    iter_sampling = 500,
    refresh = 500,
    max_treedepth = 20,
    adapt_delta = 0.99)

#Save draws
simple_draws_df <- as_draws_df(samples_simple$draws())

#print model summary
samples_simple$summary()
```

```{r}
#Plotting model quality
plot_simple_sigma <- ggplot(simple_draws_df, aes(.iteration, sigma, group=.chain, color=.chain)) +
  geom_line()+
  theme_classic() + 
  labs(title = 'Simple Bayes: Sigma')

#Print model diagnostics
samples_simple$cmdstan_diagnose()
```

#Weighted Bayes for one single participant, 103

```{r}
#Import stan-file
file <- file.path("W8_weightedBayes_single.stan")

#Compiling
mod_weighted <- cmdstan_model(file, cpp_options = list(stan_threads = TRUE), pedantic = TRUE)
```

```{r}
#Sampling
samples_weighted_single <- mod_weighted$sample(
    data = data_single,
    fixed_param = FALSE,
    seed = 123,
    chains = 2,
    parallel_chains = 2,
    threads_per_chain = 2,
    iter_warmup = 1000,
    iter_sampling = 1000,
    refresh = 1000,
    max_treedepth = 20,
    adapt_delta = 0.99)

#Save draws
weighted_draws_df_single <- as_draws_df(samples_weighted$draws())

#Print model summary
samples_weighted_single$summary()
```

```{r}
#Plotting model quality for weight1
ggplot(weighted_draws_df_single, aes(.iteration, weight1, group=.chain, color=.chain)) +
geom_line()+
theme_classic()

#Plotting model quality for weight2
ggplot(weighted_draws_df_single, aes(.iteration, weight2, group=.chain, color=.chain)) +
geom_line()+
theme_classic()

#Print model diagnostics
samples_weighted_single$cmdstan_diagnose()
```

#Weighted Bayes for 10 participants, multi-level model

```{r}
#Create data 
choices <- data_subset %>% 
  subset(select=c(ID, SecondRating))%>%
  group_by(ID)%>%
  mutate(row = row_number()) %>% 
  pivot_wider(names_from = ID, values_from = SecondRating) %>%
  select(!(row))

SourceSelfs <- data_subset %>% 
  subset(select=c(ID, FirstRating))%>%
  group_by(ID)%>%
  mutate(row = row_number()) %>% 
  pivot_wider(names_from = ID, values_from = FirstRating) %>%
  select(!(row))

SourceOthers <- data_subset %>% 
  subset(select=c(ID, OtherRating))%>%
  group_by(ID)%>%
  mutate(row = row_number()) %>% 
  pivot_wider(names_from = ID, values_from = OtherRating) %>%
  select(!(row))

#run on data for the 10 participants
data_10_levels <- list(
  trials = max(data_subset$Trial_Round2), 
  participants = length(unique(data_subset$ID)),
  choice = choices/9,
  SourceSelf = SourceSelfs/9,
  SourceOther = SourceOthers/9
  )

#adding information of specific group
data_10_levels_advanced <- list(
  trials = max(data_subset$Trial_Round2), 
  participants = length(unique(data_subset$ID)),
  choice = choices/9,
  SourceSelf = SourceSelfs/9,
  SourceOther = SourceOthers/9,
  schizo = data_subset$schizo,
  control = data_subset$control
  )
```

```{r}
#Import stan-file
file <- file.path("W8_weightedBayes.stan")

#Compiling
mod_weighted <- cmdstan_model(file, cpp_options = list(stan_threads = TRUE), pedantic = TRUE)
```

```{r}
#Sampling
samples_weighted <- mod_weighted$sample(
    data = data_10_levels,
    fixed_param = FALSE,
    seed = 123,
    chains = 2,
    parallel_chains = 2,
    threads_per_chain = 2,
    iter_warmup = 500,
    iter_sampling = 500,
    refresh = 10,
    max_treedepth = 15,
    adapt_delta = 0.99)
```


```{r}
#Save draws
weighted_draws_df <- as_draws_df(samples_weighted$draws())

#Print model summary
samples_weighted$summary()

#Plotting model quality for weight1
plot_w1 <- ggplot(weighted_draws_df, aes(.iteration, weight1M, group=.chain, color=.chain)) + 
  geom_line()+ 
  theme_classic() + 
  labs(title = 'Weighted Bayes: W1')

#Plotting model quality for weight2
plot_w2 <- ggplot(weighted_draws_df, aes(.iteration, weight2M, group=.chain, color=.chain)) + 
  geom_line()+ 
  theme_classic()+ 
  labs(title = 'Weighted Bayes: W2')

#Plotting model quality for sigma
plot_sigma <- ggplot(weighted_draws_df, aes(.iteration, sigma, group=.chain, color=.chain)) + 
  geom_line()+ 
  theme_classic()+ 
  labs(title = 'Weighted Bayes: Sigma')

plot_simple_sigma + plot_w1+plot_w2 + plot_sigma

#Print model diagnostics
samples_weighted$cmdstan_diagnose()
```


##Plotting posteriors
```{r}
#Plotting prior and posterior for weights: Has the model learned from the data? 
p1 <- ggplot(weighted_draws_df) +
  geom_density(aes(w1), fill="blue", alpha=0.3) + 
  geom_density(aes(w1_prior_t), fill="red", alpha=0.3) +   xlab("w1") +
  ylab("Posterior Density") +
  theme_classic() + 
  labs(title = 'Weighted Bayes: Prior and posterior distribution for W1')

#Plotting prior and posterior for weights: Has the model learned from the data? 
p2 <- ggplot(weighted_draws_df) +
  geom_density(aes(w2), fill="blue", alpha=0.3) + 
  geom_density(aes(w2_prior_t), fill="red", alpha=0.3) +   xlab("w2") +
  ylab("Posterior Density") +
  theme_classic() + 
  labs(title = 'Weighted Bayes: Prior and posterior distribution for W2')

#Plotting posteriors for sigma
p3 <- ggplot(weighted_draws_df) + 
    geom_density(aes(sigma), fill="blue", alpha=0.3) + 
  theme_classic() + 
  labs(title = 'Weighted Bayes: Posterior distribution for sigma')

#Plotting posteriors for tau
p4 <- ggplot(weighted_draws_df) + 
    geom_density(aes(`tau[1]`), fill="blue", alpha=0.3) + 
    geom_density(aes(`tau[2]`), fill="green", alpha=0.3) +
  theme_classic() + 
  labs(title = 'Weighted Bayes: Posterior distributions for tau')


p1 + p2 + p3 + p4

#Plotting posterior predictions vs. actual ratings
p5 <- ggplot() + 
  geom_histogram(aes(data$SecondRating[data$ID == 103]), color="darkblue", fill="blue", alpha=0.3) + 
  geom_histogram(aes(round(weighted_draws_df$`posterior_preds[1]`*9, 0)[1:153]), color="green", fill="green", alpha=0.3) + 
  xlab("Predicted ratings out of 137 trials") + 
  ylab("Posterior Density") + 
  theme_classic() + 
  labs(title = 'Posterior predictions vs. actual ratings for participant 103')


#Prior and posterior predictions for participant 1
p6 <- ggplot(weighted_draws_df) +
#  geom_histogram(aes(data_all_levels$choice[1]*9)) + 
  geom_histogram(aes(`posterior_preds[1]`*9),
  color="darkblue", fill="blue", alpha=0.3) + xlab("Predicted ratings out of 137 trials") + 
  geom_histogram(aes(`prior_preds[1]`*9),
  color="darkblue", fill="red", alpha=0.3) + xlab("Predicted ratings out of 137 trials") + 
  ylab("Posterior Density") + 
  theme_classic() + 
  labs(title = 'Prior and posterior predictions for participant 103')


p6 + p5
```

#Weighted Bayes for all participants with advanced model (two levels)

```{r}
#Import stan-file
file <- file.path("W8_weightedBayes_advanced.stan")

#Compiling
mod_weighted <- cmdstan_model(file, cpp_options = list(stan_threads = TRUE), pedantic = TRUE)
```

```{r}
#Sampling
samples_weighted_advanced <- mod_weighted$sample(
    data = data_10_levels_advanced,
    fixed_param = FALSE,
    seed = 123,
    chains = 2,
    parallel_chains = 2,
    threads_per_chain = 2,
    iter_warmup = 500,
    iter_sampling = 500,
    refresh = 10,
    max_treedepth = 20,
    adapt_delta = 0.99)

#Save draws
draws_df_advanced <- as_draws_df(samples_weighted_advanced$draws())

#Print model summary
samples_weighted_advanced$summary()
```

```{r}
#Plotting prior and posterior for weights: Has the model learned from the data? 
p1 <- ggplot(draws_df_advanced) +
  geom_density(aes(w1S), fill="blue", alpha=0.3) + 
  geom_density(aes(w1C), fill="green", alpha=0.3) + 
  geom_density(aes(w1_prior_t), fill="red", alpha=0.3) +   xlab("w1") +
  ylab("Posterior Density") +
  theme_classic() + 
  labs(title = 'Weighted Bayes: Prior and posterior distribution for W1')

#Plotting prior and posterior for weights: Has the model learned from the data? 
p2 <- ggplot(draws_df_advanced) +
  geom_density(aes(w2S), fill="blue", alpha=0.3) + 
    geom_density(aes(w2C), fill="green", alpha=0.3) + 
  geom_density(aes(w2_prior_t), fill="red", alpha=0.3) +   xlab("w2") +
  ylab("Posterior Density") +
  theme_classic() + 
  labs(title = 'Weighted Bayes: Prior and posterior distribution for W2')

#Plotting posteriors for sigma
p3 <- ggplot(draws_df_advanced) + 
    geom_density(aes(sigmaS), fill="blue", alpha=0.3) +
  geom_density(aes(sigmaC), fill="green", alpha=0.3) +
  theme_classic() + 
  labs(title = 'Weighted Bayes: Posterior distribution for sigma')

#Plotting posteriors for tau
p4 <- ggplot(draws_df_advanced) + 
    geom_density(aes(`tauS[1]`), fill="orange", alpha=0.3) + 
   geom_density(aes(`tauC[1]`), fill="purple", alpha=0.3) + 
    geom_density(aes(`tauS[2]`), fill="pink", alpha=0.3) +
    geom_density(aes(`tauC[2]`), fill="yellow", alpha=0.3) +
  theme_classic() + 
  labs(title = 'Weighted Bayes: Posterior distributions for tau')


p1 + p2 + p3 + p4

#Plotting posterior predictions vs. actual ratings
p5 <- ggplot() + 
  geom_histogram(aes(data$SecondRating[data$ID == 103]), color="darkblue", fill="blue", alpha=0.3) + 
  geom_histogram(aes(round(draws_df_advanced$`posterior_preds[1]`*9, 0)[1:153]), color="green", fill="green", alpha=0.3) + 
  xlab("Predicted ratings out of 137 trials") + 
  ylab("Posterior Density") + 
  theme_classic() + 
  labs(title = 'Posterior predictions vs. actual ratings for participant 103')


#Prior and posterior predictions for participant 1
p6 <- ggplot(draws_df_advanced) +
#  geom_histogram(aes(data_all_levels$choice[1]*9)) + 
  geom_histogram(aes(`posterior_preds[1]`*9),
  color="darkblue", fill="blue", alpha=0.3) + xlab("Predicted ratings out of 137 trials") + 
  geom_histogram(aes(`prior_preds[1]`*9),
  color="darkblue", fill="red", alpha=0.3) + xlab("Predicted ratings out of 137 trials") + 
  ylab("Posterior Density") + 
  theme_classic() + 
  labs(title = 'Prior and posterior predictions for participant 103')


p6 + p5
```


```{r}
#Plotting model quality for weight1
p1S <- ggplot(draws_df_advanced, aes(.iteration, weight1MS, group=.chain, color=.chain)) +
geom_line()+
theme_classic() + 
  labs(title = 'Weighted Advanced Bayes: W1S')

p1C <- ggplot(draws_df_advanced, aes(.iteration, weight1MC, group=.chain, color=.chain)) +
geom_line()+
theme_classic() + 
  labs(title = 'Weighted Advanced Bayes: W1C')

#Plotting model quality for weight2
p2S <- ggplot(draws_df_advanced, aes(.iteration, weight2MS, group=.chain, color=.chain)) +
geom_line()+
theme_classic() + 
  labs(title = 'Weighted Advanced Bayes: W2S')

#Plotting model quality for weight2
p2C <- ggplot(draws_df_advanced, aes(.iteration, weight2MC, group=.chain, color=.chain)) +
geom_line()+
theme_classic() + 
  labs(title = 'Weighted Advanced Bayes: W2C')

p3C <- #Plotting model quality for weight2
ggplot(draws_df_advanced, aes(.iteration, sigmaC, group=.chain, color=.chain)) +
geom_line()+
theme_classic() + 
  labs(title = 'Weighted Advanced Bayes: SigmaC')

p3S <- #Plotting model quality for weight2
ggplot(draws_df_advanced, aes(.iteration, sigmaS, group=.chain, color=.chain)) +
geom_line()+
theme_classic() + 
  labs(title = 'Weighted Advanced Bayes: SigmaS')

p1S + p2S + p3S + p1C + p2C + p3C

#Print model diagnostics
samples_simple$cmdstan_diagnose()
```

#Compare models
```{r}
#Calculate loo
Loo1 <- samples_simple$loo(save_psis = TRUE, cores = 2)
plot(Loo1)

Loo2 <- samples_weighted$loo(save_psis = TRUE, cores = 2)
plot(Loo2)

Loo3 <- samples_weighted_advanced$loo(save_psis = TRUE, cores = 2)
plot(Loo3)

#Compare models
loo_compare(Loo1, Loo2, Loo3)
```


---NOTES FROM CLASS

change ~ feedback
, so:
2rating ~ logit(1rating) + logit(otherrating)

^^ but this has issues!:

BUT BIAS/POTENTIAL CONFOUND: not all feedbacks are possible! (e.g. if rate 8, can only get negative (or 0) feedback)
- reg to the mean? -> how to discriminate btw going down from an 8 rating due to reg to mean, or due to conformity?


SECOND POINT:
prev model was Bernoulli, 0 or 1
But now we need to change the family/shape of the outcome
recommended for assignment:
- go with normal distribution (not unproblematic, since it's discrete data... but for now, fuck it).
- a function of mu (mean expected outcome) and sigma (not part of the model).
mu is logit(first rating) + logit(peerrating). deterministic in simple Bayes, just one value.
Stan doesn't like sigma of 0...
We should put sigma in as a parameter to be estimated! It's the avg error the model is making when predicting the data!
So the parameters (parameters to be estimated) AND model (form of the model) part of stan have to be filled. A model that actually estimates sigma.

we should not have fixed parameters = TRUE, since sigma isn't fixed


BIASES:
- ID plots also show: people differ in how much they use the rating scale