---
title: "Class 4"
author: "KK"
date: '2022-02-23'
output: html_document
---
```{r}
library(pacman)
p_load(tidyverse, here, posterior, cmdstanr, boot, brms)
```

#Implementing STAN code for random agent
```{r}
data1 <- read.csv('bias_detector_agent_random_agent.csv')

data <- list(
  n = 100, 
  k = data1$Other[0:100]
)
```

# Simple model
```{r}
stan_file <- write_stan_file("
// This Stan model infers a rate (theta) from a number of trials (n) and successes (k)

// The input data is two integer numbers: n and k.
data {
  int<lower=1> n; // n of trials (there has to be at least 1 to have observable data) 
  array[n]int k;  // choices
}

// The parameters accepted by the model. Our model accepts only theta, the rate, 
// which is bound at 0 (no chances of success) and 1 (always success)
parameters {
  real<lower=0, upper=1> theta;
}

// The model to be estimated; prior and likelihood
model {
  // The prior for theta is a uniform distribution between 0 and 1
  theta ~ beta(1, 1);
  
  // The model consists in a binomial distribution with a rate theta, 
  // and a number of trials n generating k successes
  k ~ binomial(n, theta);
}


")

```

To get the estimates on a probability scale, add the following : 

generated_quantities {
  real<lower = 0, upper = 1> theta_p;
  theta_p = inv_logit(theta);
}

```{r}
mod <- cmdstan_model(stan_file, cpp_options = list(stan_threads = TRUE), pedantic = TRUE)


samples <- mod$sample(
  data = data,
  seed = 123,
  chains = 2,
  parallel_chains = 2,
  threads_per_chain = 2,
  iter_warmup = 2000,
  iter_sampling = 2000,
  refresh = 500,
  max_treedepth = 20,
  adapt_delta = 0.99)

samples$summary()
```


#Implementing STAN code for agent: WSLS
```{r}

data1 <- read.csv('bias_detector_agent_wsls_agent.csv')
#data1 <- read.csv('Assignment 2_ACM/bias_detector_agent_wsls_agent.csv')

data1$Feedback_Other <- 1 - data1$Feedback_Self[0:120]

#Recoding variables to stay and leave bias: 1 = heads, -1 = tails
data1$StayBias[data1$Feedback_Other == 1 & data1$Other == 1] <- 1
data1$StayBias[data1$Feedback_Other == 1 & data1$Other == 0] <- -1
data1$StayBias[data1$Feedback_Other == 0] <- 0

data1$LeaveBias[data1$Feedback_Other == 0 & data1$Other == 1] <- -1
data1$LeaveBias[data1$Feedback_Other == 0 & data1$Other == 0] <- 1
data1$LeaveBias[data1$Feedback_Other == 1] <- 0


data <- list(
  n = 120, 
  k = data1$Other[0:120],
  f_stay = data1$StayBias[0:120],
  f_leave = data1$LeaveBias[0:120]
)
```


# WSLS model
```{r}
stan_file <- write_stan_file("
// This Stan model infers a rate (theta) from a number of trials (n) and successes (k)

// The input data is two integer numbers: n and k.
data {
  int <lower=1> n; // n of trials 
  array[n]int k;  // choices
  vector<lower=-1, upper=1>[n] f_stay; //stay bias
  vector<lower=-1, upper=1>[n] f_leave; //leave bias
}

// The parameters accepted by the model. Our model accepts only theta, the rate, 
// which is bound at 0 (no chances of success) and 1 (always success)
parameters {
  real<lower=0, upper=1> alpha;
  real<lower=0, upper=1> beta_stay;
  real<lower=0, upper=1> beta_leave;
}

transformed parameters{
  vector[n] theta;
  theta = alpha + (beta_stay*f_stay)+ (beta_leave*f_leave); //multiplying the paramaters we want to estimate on the data
}

// The model to be estimated; prior and likelihood
model {
  // The prior for theta is a uniform distribution between 0 and 1
  target += normal_lpdf(alpha | 0, 1);
  target += normal_lpdf(beta_stay | 0, 0.3);
  target += normal_lpdf(beta_leave | 0, 0.3);

  // The model consists in a binomial distribution with a rate theta, 
  // and a number of trials n generating k successes
  target += bernoulli_logit_lpmf(k | theta);
}

generated quantities {
  vector[n] theta_p;
  theta_p = inv_logit(theta);
}

")

```

Question for Riccardo: in generated quantities, should theta_p be a real number or a vector? You do both in the slides


```{r}
mod1 <- cmdstan_model(stan_file, cpp_options = list(stan_threads = TRUE), pedantic = TRUE)


samples <- mod1$sample(
  data = data,
  seed = 123,
  chains = 2,
  parallel_chains = 2,
  threads_per_chain = 2,
  iter_warmup = 2000,
  iter_sampling = 2000,
  refresh = 500,
  max_treedepth = 20,
  adapt_delta = 0.99)

samples
```

The samples gives a theta for each trial x 2? 

#Questions: 
- What is the difference between vector and array?

- How to get the following to work? 

transformed_parameters{
  vector[n] theta;
  theta = b0 + b1 + b2;
}

generated_quantities {
  real<lower = 0, upper = 1> theta_p;
  theta_p = inv_logit(alpha + beta_stay + beta_leave);
}

- What does the output mean? 


# Class 5
 In today’s class you will have to rely on your stan model from last week to
§ Include output variables for prior and for predictive checks
§ Include a prior sensitivity plot
§ Perform parameter recovery, including a test of trials needed to *adequately* recover the true parameter values
§ N.B. this might include many loops: range of true parameter values, range of noise levels, range of trials, range of n agents within the same condition, range of prior parameters. This could take forever to run. So you are allowed to only pick a few (hint: true parameter values and range of trial n is all is required)


generated quantities{
  real<lower=0, upper=1> theta_prior; real<lower=0, upper=1> theta_posterior;
  theta_prior = inv_logit(normal_rng(0,1));
theta_posterior = inv_logit(theta); }


```{r}
prior_mean_bstay <- seq(-3, 3, .5)
prior_sd_bstay <- seq(0.1, 1, 0.1)

priors <- expand.grid(prior_mean_bstay, prior_sd_bstay)
priors <- tibble(prior_mean_bstay = priors$Var1, prior_sd_bstay$Var2)
```



